Reducing retrieval error in MAIAC AOD with the `Earth_obs_cleaning` machine-learning workflow: Results from CONUS

### 2023-08-17 writing/CONUS_AOD.qmd
Show the hyperparameters selected for the full model.
Made error envelopes more like they used to be.

We use Nelder-Mead optimization to construct new error envelopes with coverage as close to 2/3 as possible for each of two subsets of the data: observations less than or equal to 0.6, and observations greater than 0.6. The results are an envelope with `r f = \(pred) {ps = empirical.error.envelope(obs = dt$y.ground, pred)$par; sprintf("additive part %.03f and multiplicative part %.03f", ps[1], ps[2])}; f(dt$y.sat)` for the raw satellite values, and an envelope with `r f(dt$y.ground.pred)` for our predictions. The original error envelope (reported in the AMT MAIAC publication), applied to the raw satellite values, has coverage `r x = envelope.tester(obs = dt$y.ground, pred = dt$y.sat)(.05, .1); sprintf("%.03f", x["lo"])` in the low subset and `r sprintf("%.03f", x["hi"])` in the high subset.

@@

## Maps of new predictions

>>>>

We use Nelder-Mead optimization to construct new error envelopes with coverage as close to 2/3 as possible for each of two subsets of the data: observations less than or equal to 0.6, and observations greater than 0.6. The results are an envelope with `r f = \(pred) {o = empirical.error.envelope(obs = dt$y.ground, pred); stopifnot(o$convergence == 0); sprintf("additive part %.03f and multiplicative part %.03f", o$par[1], o$par[2])}; f(dt$y.sat)` for the raw satellite values, and an envelope with `r f(dt$y.ground.pred)` for our predictions. The original error envelope (reported in the AMT MAIAC publication), applied to the raw satellite values, has coverage `r x = envelope.tester(obs = dt$y.ground, pred = dt$y.sat)(.05, .1); sprintf("%.03f", x["lo"])` in the low subset and `r sprintf("%.03f", x["hi"])` in the high subset.

@@

## New predictions

For the model trained on all the data, the selected hyperparameters were `r v = tar_read(model.full)$hyperparams; paste0(collapse = ", ", sprintf("%s = %s", names(v), v))`.
